\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable}

\begin{document}

\textbf{\large \noindent Brownian coagulation kernel based on M.Z. Jacobson, Fundamentals of Atmospheric Modeling, second edition, Cambridge University Press, 2005 and J.H. Seinfeld and S.N. Pandis, Atmospheric Chemistry and Physics: From Air Pollution to Climate Change, second edition, John Wiley \& Sons, Inc., 2006.}

\section{Symbol list}
\label{sec:symbol-list}

\newcommand{\rr}{\raggedright}
\newcommand{\tn}{\tabularnewline\hline}
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{|l|p{5.5cm}|l|l|p{4.5cm}|}
\hline \textbf{Symbol} & \textbf{Meaning} & \textbf{Type} & \textbf{Units} &  \textbf{Reference} \tn
\hline \endhead
$C_{c}$  & Cunningham slip-flow correction & function & 1 & \ref{eq:cc},Jacobson 15.30 \tn
$D_{\textrm{p},i}$ & particle $i$ diffusion coefficient & function & & eq. \ref{eq:diff}, Jacobson 15.29 \tn
$\delta_i $  & mean distance from the center of a sphere reached by particle $i$ leaving the 
  sphere's surface and traveling a distance of the particle mean free path $\lambda_{{\rm p},i}$ 
  & function & m & eq. \ref{eq:delta}, Jacobson 15.34 \tn 
$\eta_{\rm a} $ & dyanmic viscosity of air & function & kg m$^{-1}$ s$^{-1}$ 
  &eq. \ref{eq:viscod}, Jacobson 4.54 \tn
$k_{\rm B}$ & Boltzmann's constant & constant & 1 & \tn
$K_{i,j}^{\rm B}$ & brownian collision kernel for particles $i$ and $j$   & function & m$^3$ s$^{-1}$ 
  &  eq. \ref{eq:bckernel}, Jacobson 15.33 \tn
$\mathrm{Kn}$ & Knudsen number & function & 1 & eq. \ref{eq:knudsen}, Jacobson 15.23 \tn
$\lambda_{\rm a}$ & \rr mean free path of air molecule    &   function      & m     &  eq. \ref{eq:mfp}, Jacobson 15.24  \tn
$\lambda_{\textrm{p},i}$ & mean free path for particle $i$ & function & m & eq. \ref{eq:particlemfp}, Jacobson 15.34 \tn
$M_{\rm a}$ &molecular weight of air & constant & kg mol$^{-1}$ & \tn
$\bar{M}_{\rm a}$ & weight of an air molecule & constant & kg & eq. \ref{eq:molecule_mass} \tn
$M_{\textrm{p},i}$ & mass of particle $i$ & function & kg & \tn
$N_{\rm A}$ &Avaogadro constant & constant & mol$^{-1}$ & \tn
$\nu_{\rm a} $ & kinematic viscosity of air & function & m$^2$ s$^{-1}$  & eq. \ref{eq:viscok}, Jacobson 4.55 \tn
$\rho_{\rm a}$ & air density & function & kg m$^{-3}$ & eq. \ref{eq:rhoair} \tn
$r_i$ & \rr radius of particle $i$  &   dynamic & m  &   eq. \ref{eq:particleradius} \tn
$R$ & universal gas constant & constant & J mole$^{-1}$ K$^{-1}$ & \tn
$T$  & current environmental temperature & prescribed & K &  \tn
$\bar{v}_{\rm a}$ & thermal speed of air molecule & function & m s$^{-1}$ & \tn
$\bar{v}_{\textrm{p},i}$ & \rr thermal speed of particle $i$ in air  &  function  &  m s$^{-1}$ 
  & eq. \ref{eq:particlespeed}, Jacobson 15.32\tn
\end{longtable}

\section{Equations}
\label{sec:equations}

\begin{align}
r_i & = \left(\frac{3V_i}{4\pi}\right)^{\frac{1}{3}} \label{eq:particleradius} \\
\bar{v}_{\textrm{p},i} & = \sqrt{ \frac{8 k_{\textrm{B}}T}{\pi M_{\textrm{p},i}}} \label{eq:particlespeed} \\
D_{\textrm{p},i} & = \frac{k_{\textrm{B}}T}{6 \pi r_i \eta_{\textrm{a}}} C_{\rm c}  \label{eq:diff}\\
C_{\textrm{C}}  & = 1 + \mathrm{Kn}_{\textrm{a},i} \left(1.249 + 0.42 \exp \left(-\frac{0.87}{\mathrm{Kn}_{\textrm{a},i} }\right)\right) \label{eq:cc}\\
\mathrm{Kn}_{\textrm{a},i} & = \frac{\lambda}{r_i}   \label{eq:knudsen}\\
K_{i,j}^{\rm B} & = \frac{4\pi\left(r_i + r_j \right)\left(D_{\textrm{p},i} + D_{\textrm{p}.j}\right)}
{  \frac{r_i + r_j}{r_i + r_j + \sqrt{\delta_i^2 + \delta_j^2}}
+ \frac{4\left(D_{\textrm{p},i} + D_{\textrm{p},j}\right) } { \sqrt{\bar{v}_{\textrm{p},i}^2 + \bar{v}_{\textrm{p},j}^2} \left(r_i + r_j\right)}}
\label{eq:bckernel} \\
\delta_i & = \frac{\left(2r_i + \lambda_{\textrm{p},i}\right)^3 - \left(4r_i^2 +\lambda_{\textrm{p},i}^2 \right)^{3/2}}{6 r_i \lambda_{\textrm{p},i}} - 2 r_i \label{eq:delta}\\
\lambda_{\textrm{p},i} & = \frac{8 D_{\textrm{p},i}}{\pi \bar{v}_{\textrm{p},i}} \label{eq:particlemfp}\\
\lambda_{\rm a} & = \frac{2 \nu_a}{\bar{v}_{\rm a}} \label{eq:mfp}\\
\bar{v}_{\rm a} & = \sqrt{ \frac{8 k_{\textrm{B}}T }{\pi \bar{M}_{\rm a}}}  =  \sqrt{ \frac{8 k_{\textrm{B}}T N_{\rm A}}{\pi M_{\rm a}}} \\
\bar{v}_{\textrm{p},i} & = \sqrt{ \frac{8 k_{\textrm{B}}T }{\pi \bar{M}_{\textrm{p}, i}}} \\
\eta_{\rm a} & \approx 1.8325 \times 10^{-5} \left(\frac{416.16}{T + 120}\right) \left(\frac{T}{296.16}\right)^{1.5} \label{eq:viscod}\\
\nu_{\rm a} & = \frac{\eta_{\rm a}}{\rho_{\rm a}} \label{eq:viscok}\\
\bar{M}_{\rm a} & = \frac{M_{\rm a} }{N_{\rm A}} \label{eq:molecule_mass} \\
\rho_a & = \frac{pM_{\rm a}}{RT} \label{eq:rhoair}
\end{align}

\end{document}
