\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable}

\begin{document}

\section{Symbol list}
\label{sec:symbol-list}

\newcommand{\rr}{\raggedright}
\newcommand{\tn}{\tabularnewline\hline}
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{|l|p{5.5cm}|l|l|p{4.5cm}|}
\hline 
\textbf{Symbol} & \textbf{Meaning}                                                       & \textbf{Type} & \textbf{Units}                        &  \textbf{Reference}                                \tn
\endhead
\hline 
$\alpha$ & parameter &   & 1   &      \tn
$A$ & characteristic radius of large collectors  &   &  m    &  \tn
$\beta$ & parameter & & 1 &  \tn
$\gamma$  & parameter &  & 1    &      \tn
$C_c$ & \rr Cunningham slip correction factor & function & 1 &\rr  eq. \eqref{eq:cc}, Zhang et al eq. 3\tn
$D$ & Brownian diffusion & function & m$^2$ s$^{-1}$& eq. \eqref{eq:brownian}, S\&P eq. 9.73\tn
$D_p$ & particle diameter & function & m & \tn
$E_{\textrm{B}}$  & \rr collection efficiency from Brownian diffusion  & function         & 1    &  \rr eq. \eqref{eq:eb},  Zhang et al eq. 6 \tn
$E_{\textrm{IM}}$  & \rr collection efficiency from impaction  & function         & 1    &   \rr eq. \eqref{eq:eim},          Zhang et al eq. 7c \tn
$E_{\textrm{IN}}$  & \rr collection efficiency from interception & function         & 1    &\rr   eq. \eqref{eq:ein},      Zhang et al eq. 8 \tn
$\epsilon_0$  & \rr empirical constant  & constant         & 1   &                      \tn
$k$ & \rr Von Karman constant & constant & 1 & \tn
$k_b$ & \rr Boltzmann constant & constant & 1 & \tn
$\lambda$ & mean free path of air molecules & function & m & eq. \ref{eq:lambda}\tn
$\bar{M}$ & mass of a molecule of air & constant & kg & \tn
$R_1$  & \rr correction factor for bounce-off  & function &  1    & \rr  eq. \eqref{eq:R_1}, Zhang et al eq. 9 \tn
$R_a$  & \rr aerodynamic resistance  & function & m$^{-1}$ s &  \tn
$R_s$  & \rr surface resistance  & function & m$^{-1}$ s & Zhang et al 2001 eq. 5 \tn
$\rho$ & density of particle & input & kg m$^{-3}$ &  \tn
$\rho_a$ & density of air & function & kg m$^{-3}$ & \tn
$ Sc $ & \rr Schmidt number & function & 1 &\rr  eq. \eqref{eq:sc}\tn
$ St$ & \rr Stokes number for smooth surfaces & function & 1 &\rr  eq. \eqref{eq:st_smooth}, S\&P 19.23 \tn
$ St$ & \rr Stokes number for vegetated surfaces & function & 1 & \rr eq. \eqref{eq:st_veg}, S\&P 19.24 \tn
$T$ & current environmental temperature & input & K & \tn
$u_*$ & \rr friction velocity & function & m s$^{-1}$ & \tn
$\mu$ & dynamic viscocity of air & function & kg m$^{-1}$ s$^{-1}$&\rr  eq. \eqref{eq:dynamic_visc}, Jacobson eq. 4.54 \tn
$\nu$ & kinematic viscocity of air & function & m$^2$ s$^{-1}$&\rr  eq. \eqref{eq:kinematic_visc} \tn
$\bar{v}_a$ & thermal speed of an air molecule & function & m s$^{-1}$ & eq. \eqref{eq:thermal}, Jacobson eq. 15.25 \tn
$V_d$  & \rr deposition velocity  & function & m s$^{-1}$ & eq. \eqref{eq:vd}, Zhang et al eq. 1 \tn
$V_s$  & \rr settling velocity  & function & m s$^{-1}$   &eq. \eqref{eq:vs}, Zhang et al eq. 2 \tn
\end{longtable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Equations}
\label{sec:equations}

\begin{align}
\mu & =  1.8325 \times 10^{-5}\left(\frac{416.16}{T + 120}\right)\left(\frac{T}{296.16}\right)^{1.5}\label{eq:dynamic_visc}\\
\nu & = \frac{\mu}{\rho_a}  \label{eq:kinematic_visc}\\
V_d &= V_s + \frac{1}{R_a + R_s} \label{eq:vd}\\
V_s & = \frac{\rho D_p^2gC_c}{18\mu } \label{eq:vs}\\
Sc &= \frac{\nu}{D}   \label{eq:sc} \\
St &= \frac{V_su_*^2}{g \nu } \label{eq:st_smooth}\\
St &= \frac{V_s u_*}{gA}  \label{eq:st_veg}\\
R_1 &= \exp(-St^{1/2}) \label{eq:R_1}\\
E_{\textrm{B}} &= Sc^{-\gamma}  \label{eq:eb}\\
E_{\textrm{IM}} & = \left(\frac{St}{\alpha + St}\right)^{\beta} \label{eq:eim}\\
E_{\textrm{IN}} &= \frac{1}{2} \left(\frac{D_p}{A}\right)^2 \label{eq:ein}\\
C_c & = 1 + \frac{2 \lambda}{d_p}\left(1.257 + 0.4\exp(-.55 D_p/\lambda)\right)  \label{eq:cc}\\ 
D & = \frac{kTC_c}{3 \pi \mu D_p}  \label{eq:brownian}\\
\lambda & = \frac{2 \mu}{\rho_a v_a} \label{eq:lambda}\\
\bar{v}_a & = \sqrt{\frac{8k_bT}{\pi\bar{M}}} \label{eq:thermal}
\end{align}

\section{Determining the environmental values $R_a$ and $u_*$}

Aerodynamic resistance is a contributing factor that is independent of particle size
and composition. To determine aerodynamic resistance, we use the following
based on Pasquill Stability Classes.

From Seinfeld and Pandis page 907, aerodynamic resistance for neutral stability is
\begin{equation}
R_a =
\frac{1}{\kappa u_*} \ln \left( \frac{z}{z_0} \right).
\end{equation}
Friction velocity $u_{*}$ is given by equation 16.80 in S\&P as
\begin{align}
u_* & = \frac{\kappa \bar{u}\left(z_{\rm ref}\right)}
  {\int_{z_0}^{z_{\rm ref}} \left(\Phi (z/L)/z\right)dz}.
\end{align}
Given a neutral atmosphere, this reduces to 16.67 in S\&P
\begin{align}
u_* & = \frac{\kappa \bar{u}\left(z_{\rm ref}\right)}
  \ln \left(\frac{z_{\rm ref}}{z_0}\right).
\end{align}

\section{References}
\begin{itemize}
\item Seinfeld, John H., and Spyros N. Pandis. Atmospheric Chemistry
  and Physics: From Pollution to Climate Change. John Wiley \& Sons, 2012.
\item M. Z. Jacobson,
Fundamentals of Atmospheric Modeling, Second Edition, Cambridge University Press, 2005.
\item Zhang, L., Gong, S., Padro, J., and Barrie, L.: A size-segregated
    particle dry deposition scheme for an atmospheric aerosol module,
    Atmospheric Environment, 35, 549-560, 2001.
\end{itemize}
\end{document}
