\documentclass{article}
\usepackage{amsmath}
\usepackage[margin=2cm]{geometry}
\usepackage{longtable}
\usepackage{comment}

\begin{document}

\section{Symbol list}
\label{sec:symbol-list}

\newcommand{\rr}{\raggedright}
\newcommand{\tn}{\tabularnewline\hline}
\renewcommand{\arraystretch}{1.5}
\begin{longtable}{|l|p{5.5cm}|l|l|p{4.5cm}|}
\hline \textbf{Symbol} & \textbf{Meaning}                                                       & \textbf{Type} & \textbf{Units}                        &  \textbf{Reference}                                \tn
\hline \endhead
\(i\) & species index. & index & discrete & \tn
\( A_j \) & The total surface area of the INP. & function & $m^2$ & \tn
\( A_j^\text{(i)} \) & Surface area of \( i \)th species. & function & $m^2$ & \tn
\( a_{\text{w}} \) & Water activity of the droplet in which the INP is immersed. & function & 1 & eq.~\ref{eq:4}\tn
\( a_\text{w}^\text{ice} \) & Water activity in equilibrium with ice.  & function & 1 & eq.~\ref{eq:5} \tn
\(a_\text{INAS}\) & INAS parameter for singular scheme. & constant & $K^{-1}$ & Niemand et al., 2012 \tn
\(b_\text{INAS}\) & INAS parameter for singular scheme. & constant & 1 & Niemand et al., 2012 \tn
\( \Delta t \) & Time interval.  & function & $s$ & \tn
\( e_\text{s} \) & Saturated vapor pressure with respect to water. & function & Pa & eq.~\ref{eq:2} \tn
\( e_\text{s}^\text{ice} \) & Saturated vapor pressure with respect to ice. & function & Pa & eq.~\ref{eq:3} \tn
\( H \) & Relative humidity with respect to water. & dynamics & 1 & \tn
\( J_{\text{het}} \) & A constant heterogeneous freezing rate for all particles (for the constant nucleation rate scheme only) & constant &  $m^{-2}s^{-1}$ & \tn
\( J_{\text{het}}^{(i)} \) & Heterogeneous freezing rate coefficients of the \( i \)th species. & function & $m^{-2}s^{-1}$ & eq.~\ref{eq:6} \tn
\( m_i, c_i \) & ABIFM parameters of \( i^\text{th} \) species. & constant & 1 & Knopf et al., 2013 \tn
\(n_0\) & An unit constant (=1 $m^{-2}$). & constant & $m^{-2}$ & \tn
\( N_\text{s} \) & The total number of species covering the surface of the INP. & constant & 1 & \tn
\( P_{\text{frz,}j} (\Delta t)\) & The freezing probability of $j^\text{th}$ particle within a time interval of $\Delta t$. & function & 1 & eq.~\ref{eq:1},eq.~\ref{eq:7} \tn
\(p_j\) & A random number uniformly distributed in [0,1] regarding the sampling of $j^\text{th}$ particle. & function & 1 & eq.~\ref{eq:8} \tn
\(T\) & Current environmental temperature & prescribed & $K$ & \tn
\(T_0\) & Water freezing temperature & constant & K & \verb+env_state%temp+ \tn
\(T_{\text{m,}j}\) & The freezing temperature of the $j^\text{th}$ particle. & function & K & eq.~\ref{eq:9} \tn

\end{longtable}

\begin{comment}
\( J_{\text{het}}^{(i)} \) & Heterogeneous freezing rate coefficients of the \( i \)th species. \\
        \( A_i \) & Surface area of \( i \)th species. \\
        \( A \) & The total surface area of the INP. \\
        \( \Delta t \) & Time interval. \\
        \( a_{\text{w}} \) & Water activity of the droplet in which the INP is immersed. \\
        \( a_\text{w}^\text{ice} \) & Water activity in equilibrium with ice. \\
        \( RH \) & Relative humidity with respect to water. \\
        \( e_\text{s} \) & Saturated vapor pressure with respect to water. \\
        \( e_\text{s}^\text{ice} \) & Saturated vapor pressure with respect to ice. \\
        \( m_i, c_i \) & ABIFM parameters of \( i^\text{th} \) species. \\
        \( N_\text{s} \) & The total number of species covering the surface of the INP. \\
        \hline
\end{comment}

\section{Equations}
\label{sec:equations}

\subsection{Time-dependent scheme with a constant nucleation rate}
\begin{equation}
    P_{\text{frz,}j}(\Delta t) = 1 - \exp\left(J_{\text{het}} \cdot A_j \cdot \Delta t \right) \label{eq:1}
\end{equation}

\subsection{Time-dependent ABIFM scheme}
\begin{equation}
    \begin{split}
        e_\text{s}(T) &= \exp \left\{ 54.842763 - \frac{6763.22}{T} - 4.21 * \ln{T} + 0.000367T \right.\\
        &+ \left. \tanh \left[{0.0415 \cdot (T - 218.8) \cdot (53.878 - \frac{1331.22}{T} - 9.44523 \ln{T} + 0.014025T)}\right] \right\} \label{eq:2}
    \end{split}
\end{equation}
\begin{equation}
    e_\text{s}^\text{ice} (T) = \exp \left( 9.550426 - \frac{5723.265}{T} + 3.53068 \cdot \ln{T} - 0.00728332T\right). \label{eq:3}
\end{equation}
\begin{align}
  a_{\text{w}} &= 1 \label{eq:4} \\
  a_\text{w}^\text{ice} &= \frac{e_\text{s}^\text{ice}(T)}{e_\text{s}(T)} \label{eq:5} \\
  \log_{10}J_{\text{het}}^{(i)} &= m_{\text{i}} \cdot (a_{\text{w}} - a_\text{w}^\text{ice}) + c_i \label{eq:6} \\
  P_{\text{frz,}j}(\Delta t) &= 1 - \exp\left[ -\sum_{i=1}^{N_{\text{s}}} (A_j^\text{(i)} \cdot J_{\text{het}}^{(i)}) \cdot \Delta t \right] \label{eq:7}
\end{align}

\subsection{Singular scheme}
\begin{equation}
    p_j = random() \in [0,1] \label{eq:8}
\end{equation}

\begin{equation}
    T_{\text{m,}j} = T_0 + \frac{1}{a_\text{INAS}} \left[\ln{\left( \frac{\ln{(1-p_j)} + \exp{\left(-A_j n_0 \exp{\left(-a_\text{INAS} T_0 + b_\text{INAS}\right)}\right)}}{-A_j n_0} \right)} - b_\text{INAS}\right] \label{eq:9}
\end{equation}
\end{document}
